Tungsten Disulfides and Tungsten Oxides Core-Shell NWs

### 2014-08-07 BackMatter/paper.tex
tms chapter 80/100

@@

2D wo3.\cite{Kalantar-zadeh2010a}

@@

>>>>

2D wo3.\cite{Kalantar-zadeh2010a} 
WO3 plasmon \cite{Manthiram2012}

@@

@@

\subsection{strain}

$E_{2g}$ mode is strain sensitive.

\citeauthor{Ghorbani-Asl2013} studied the strain in tubular TMDC and found a linear dependence of Raman scattering on strain (3 \si{cm^{-1}} per percentage for $E_{2g}$mode).\cite{Ghorbani-Asl2013}

\citeauthor{Virsek2007} performed a Raman-TEM integrated study on multiwalled \ce{WS2} NT with diameter \textgreater 200 nm. The tubes were synthesized using chemical transport method. Up-shift of Raman is explained by strain in the walls. This shift is not observed in the specimen by sulfurization process of oxides. Applied hydrostatic pressure is isotropic,\cite{Staiger2012} while the strain is expected to anisotropic. Strain can also be relaxed by chirality.\cite{Virsek2007}

strain effect by first-principles calculations. direct gap is only maintain in a narrow strain range (-1.3 -- 0.3 \%), \cite{Yun2012}.

Semiconducting to metallic transition in \ce{MoS2} at compressive strain of 15\% or tensile strain of 8\%; direct-to-indirect gap transition for 1L \ce{MoS2} at about 2\%. \cite{Scalise2012}

strain and Raman theoretical analysis.\cite{Chang2013a}

magnetic properties of ws2.\cite{Zhang2013j}

growth mechanism of WS2 NT:

It was found that the critical step in this process is the fast conversion of the oxide nanoparticle surface into a closed monolayer of WS2. W18O49 as an intermediate phase is observed. XRD peaks shift to monitor strain.(002) peak of nanotube shifted to lower angles, the interlayer spacing increase by about 2\% as compared to the bulk powder, likely due to the build-in strain.\cite{ZAK2009} 
$\epsilon = (a - a_0)/a_0$ =(6.4-6.16)/6.16 = 3.8\%. tensile strain ($\epsilon > 0$)

`` Nanotubes not fully converted appeared also during short
runs with higher working pressure. HRTEM observations
revealed an amorphous phase inside some of the nanotubes’
hollow cores, generally near the nanotubes tip (Fig. 5a). The
amorphous phase occupies only a small fraction of the nanotube’s
core volume. A meniscus is found to form at the contact
point between the amorphous matter and the nanotube’s walls.
Fig. 5b displays such a meniscus in the nanotube core (marked
by arrows). The presence of this meniscus indicates that this
amorphous material solidified from a molten phase during the
cool-down period of the sample. The meniscus of the amorphous
phase suggest that the amorphous matter wets the
nanotubes’ walls. Since the WS2 nanotubes are hydrophobic,
this observation indicates that a monomolecular layer of oxide
is left on the entire hollow core of the nanotubes. The nanotube
walls near the contact area with the meniscus are quite defective,
probably due to the large differences between the thermal
expansion coefficients of the WS2 and the amorphous matter,
which induces strain during the cool-down period of the
reaction product. These observations are consistent with the
notion that the amorphous material inside the core is an oxide
phase which is hydrophilic and does not wet the hydrophobic
WS2 layers''\cite{Margolin2004}

\subsection{others}

### 2014-08-07 ch-tms/tms.tex
tms chapter 80/100

Commercial available tungsten powders with different size are usually associated with purity variation as well, as already listed in Table.~\ref{tab:ch5pre}. The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs. A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence and influence of oxygen partial pressure.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{JAP-2column_Fig1.jpg}
\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500 \si{\degreeCelsius}, b) 600 \si{\degreeCelsius}, c) 650 \si{\degreeCelsius}, d) 750 \si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650 \si{\degreeCelsius}. Oxygen flow rate is 1 sccm.}
\label{fig:pdtemp}
\end{figure}

Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder. At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow. When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface. Further increase of temperature lead to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures. It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{JAP-2column_Fig3.jpg}
\caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow. a) 17 $\mu m$, b) 32 $\mu m$, c) 3.3 $\mu m$, d) 1.5 $\mu m$.}
\label{fig:pdsize}
\end{figure}

Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions. In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micro particles as well as some short tiny NWs, whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature. This dramatic difference could be explained in terms of surface energy and oxygen diffusion. With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lower the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favor the NWs formation on 3N5 powder. When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition. Since the size distribution of 3N powder is more uniform than that of 3N5 powder, the author employed the former as seeds.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{JAP-2column_Fig2.jpg}
\caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm. The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
\label{fig:pdoxy}
\end{figure}

@@

% seeded edx 
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{wo3_seed_edx}
\caption[Composition analysis on seeded growth \ce{WO3} NWs]{EDX spectroscopy on seeded growth \ce{WO3} NWs.}
\label{fig:woedx}
\end{figure}
Energy-dispersive X-ray spectroscopy (EDX) analysis on the seeded growth \ce{WO3} NWs is shown in Fig.~\ref{fig:woedx}. Only W and O elements were detected on the NW array. The background level from 3 to 8 keV was a manifestation of the continuous components of W X-ray spectrum.

@@

To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into ethanol solution and then dipped onto polydimethylsiloxane (PDMS) support. A home-built micromanipulator with proble tip (tungsten, 100nm point radius, Micromaipulator) was used to pick up the core-shell NWs and transfer them onto TEM grids (Lacey C, 300 mesh, Cu, 01895-F Ted Pella, Inc) under 100x objective. The steps are visualized in Fig.~\ref{fig:ch5ws2trans}. 
% ws2 transfer
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{ws2trans}
\caption[Manipulating core-shell NWs]{Core-shell nanowires transfer steps. }
\label{fig:ch5ws2trans}
\end{figure}

The transferred NWs were first examined using TEM to identify the \ce{WS2} layers configuration and the associated geometrical orientation. Then the core-shell NWs on TEM grids were probed under Raman in a location-resolved manner. To perform TEM and Raman analysis on individual NWs, only one NW was placed in each cell on the TEM grid (65 $\times$ 65 $\mu$m). And the low magnification TEM images and optical images were compared to map the NW location and orientation. The carbon film patterns served as a unique background to resolve possible ambiguity. An example is given in Fig.~\ref{fig:ch5ws2map}. 
% ws2 map
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{ws2map}
\caption[Mapping core-shell NWs]{Core-shell nanowires mapping. }
\label{fig:ch5ws2map}
\end{figure}

% fig Raman TEM
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_tem_ram}
\caption[TEM-Raman integrated characterization on core-shell NWs]{TEM-Raman integrated results on one core-shell nanowires. (}
\label{fig:ch5ws2ram}
\end{figure}

a)-(c) \ce{WS2} layer number variation from bulk to 2L. (d) Associated Raman spectra with site1-3 corresponding to HRTEM images (a)-(c), respectively. (e) Multi-peak Lorentzian fitting on Raman spectrum site 3 with inset showing layer number dependent intensities ratio of $I_{2LA}/I_{A_{1g}}$ under 532 nm excitation.

@@

growth mechanism of WS2 NT\cite{ZAK2009} 
It was found that the critical step in this process is the fast conversion of the oxide nanoparticle surface into a closed monolayer of WS2. W18O49 as an intermediate phase is observed. XRD peaks shift to monitor strain.

>>>>

Commercial available tungsten powders with different size are usually associated with purity variation as well, as already listed in Table.~\ref{tab:ch5pre}. The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs. A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence and influence of oxygen partial pressure.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{JAP-2column_Fig1.jpg}
\caption[W powder oxidation: temperature effect]{SEM graphs of 99.9\% (3N) tungsten powder oxidization at different temperatures of a) 500 \si{\degreeCelsius}, b) 600 \si{\degreeCelsius}, c) 650 \si{\degreeCelsius}, d) 750 \si{\degreeCelsius}, showing the optimal temperature for local formation of nanowires is between 600--650 \si{\degreeCelsius}. Oxygen flow rate is 1 sccm.}
\label{fig:pdtemp}
\end{figure}

Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder. At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow. When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface. Further increase of temperature lead to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures. It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{JAP-2column_Fig3.jpg}
\caption[W powder oxidation: size effect]{SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow. a) 17 $\mu m$, b) 32 $\mu m$, c) 3.3 $\mu m$, d) 1.5 $\mu m$.}
\label{fig:pdsize}
\end{figure}

Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions. In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface is primarily covered with sub-micro particles as well as some short tiny NWs, whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature. This dramatic difference could be explained in terms of surface energy and oxygen diffusion. With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lower the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favor the NWs formation on 3N5 powder. When it comes to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition. Since the size distribution of 3N powder is more uniform than that of 3N5 powder, the author employed the former as seeds.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{JAP-2column_Fig2.jpg}
\caption[W powder oxidation: oxygen pressure]{SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm. The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
\label{fig:pdoxy}
\end{figure}

@@

% seeded edx 
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{wo3_seed_edx}
\caption[Composition analysis on seeded growth \ce{WO3} NWs]{EDX spectroscopy on seeded growth \ce{WO3} NWs.}
\label{fig:woedx}
\end{figure}
Energy-dispersive X-ray spectroscopy (EDX) analysis on the seeded growth \ce{WO3} NWs is shown in Fig.~\ref{fig:woedx}. Only W and O elements were detected on the NW array. The background level from 3 to 8 keV was a manifestation of the continuous components of W X-ray spectrum.

@@

To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into ethanol solution and then dipped onto polydimethylsiloxane (PDMS) support. A home-built micromanipulator with proble tip (tungsten, 100nm point radius, Micromaipulator) was used to pick up the core-shell NWs and transfer them onto TEM grids (Lacey C, 300 mesh, Cu, 01895-F Ted Pella, Inc) under 100x objective. The steps are visualized in Fig.~\ref{fig:ch5ws2trans}. 
% ws2 transfer
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{ws2trans}
\caption[Manipulating core-shell NWs]{Core-shell nanowires transfer steps. }
\label{fig:ch5ws2trans}
\end{figure}

The transferred NWs were first examined using TEM to identify the \ce{WS2} layers configuration and the associated geometrical orientation. Then the core-shell NWs on TEM grids were probed under Raman in a location-resolved manner. Only those core-shell NWs exhibiting relative smooth \ce{WS2} wall number transition was used in subsequent Raman measurement (wall number and layer number were used interchangeably in this work, but 1 wall is not equal to 1 layer due to the tubular structure). To perform TEM and Raman analysis on individual NWs, only one NW was placed in each cell on the TEM grid (65 $\times$ 65 $\mu$m). And the low magnification TEM images and optical images were compared to map the NW location and orientation. The carbon film patterns served as a unique background to resolve possible ambiguity. An example is given in Fig.~\ref{fig:ch5ws2map}. 
% ws2 map
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{ws2map}
\caption[Mapping core-shell NWs]{Core-shell nanowires mapping. }
\label{fig:ch5ws2map}
\end{figure}

Fig.~\ref{fig:ch5ws2ram}a-d depict typical \ce{WO3}-\ce{WS2} NWs used in TEM-Raman integrated study. The diameter of these core-shell NWs is around 100 nm and the length around 10 $\mu$m, allowing for up to five distinctive Raman scattering sites. Fig.~\ref{fig:ch5ws2ram}e shows the associated Raman spectra acquired on core-shell NWs using 532 nm excitation. Two strong peaks were observed between 300 and 450 \si{cm^{-1}}. The resonant nature\cite{Stacy1985} of Raman shift is recognized by the broad band at about 350 \si{cm^{-1}}.  Recent theoretical\cite{Molina-Sanchez2011} and experimental\cite{Staiger2012} studies on 2D and tubular \ce{WS2} agree this band consist of first order mode $E_{2g}^1$ and second order mode $2LA(M)$, although there is still discrepancy on the exact symmetry assignment, \emph{i.e.}, the presence of $E_{2g}^1(M)$ mode.\cite{Berkdemir2013,Peimyoo2013}. The other peak at about 420 \si{cm^{-1}} is assigned to $A_{1g}$ mode in both bulk\cite{Sekine1980} and few layer \ce{WS2}. Tubular \ce{WS2} structure can be viewed as rolling up the planar \ce{WS2} sheet, and new Raman features arise subsequently, \emph{e.g.}, a shoulder mode emerges on the low frequency side of $A_{1g}$ mode. Theoretical investigation suggests assigning this mode as $B_{1u}$, the Davydov doublet of $A_{1g}$ mode.\cite{Ataca2012} And experimental study confirmed this $B_{1u}$ mode arise from structural disorder of \ce{WS2} layers, and the intensity ratio between $B_{1u}$ and $A_{1g}$ strongly depended on excitation wavelength.\cite{Staiger2012} This study observed $B_{1u}$ mode under 532 nm is much less prominent than that of 632 nm, in consistent with previous reports.\cite{Krause2009,Krause2009a}

% fig Raman TEM
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_tem_ram}
\caption[TEM-Raman integrated characterization on core-shell NWs]{(a)-(d) HRTEM images on several NWs showing the \ce{WS2} wall number variation from one to about ten. (e) Raman spectra acquired from core-shell NWs supported on TEM grids, indicating a sharp contrast between the in-plane and out-of-plane vibrations. Notice that the Raman spectra primarily arise from the outer \ce{WS2} shell, and only weak Raman shift at about 800 \si{cm^{-1}} were observed at some bare core region (not shown here). (f) Layer number dependence on averaged intensity ratio between the in-plane and out-of-plane Raman bands. }
\label{fig:ch5ws2ram}
\end{figure}

Multi-peak Lorentzian fitting was also attempted on spectra shown in Fig.~\ref{fig:ch5ws2ram}e. Similar trend was found between the apparent peak ratio and the de-convolution value, as shown in Fig.~\ref{fig:ch5ws2pr}. For a qualitative purpose, the overall intensity ratio $I_{E/A}$ between in-plane E band ($E_{2g}^1+2LA$) and out-of-plane A band ($A_{1g}+B_{1u}$) is sufficient. This value is then extracted to correlate with layer number variation. Multiple Raman spectra for each layer were averaged, as shown in Fig.~\ref{fig:ch5ws2ram}f.

% fig Raman TEM
\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{ws2_peak_ratio}
\caption[Multi-peak Lorentzian fitting on core-shell NWs]{Comparison of apparent peak ratio and de-convolution value.}
\label{fig:ch5ws2pr}
\end{figure}

The intensity ratio $I_{E/A}$ decreases monotonically with the increase of \ce{WS2} wall number, a similar trend as observed on 2D few layer \ce{WS2}. The exact value of $I_{E/A}$ shows modest difference with 2D sheet, which is attributed to the suspended configuration of current core-shell NWs specimen and the presence of \ce{WO3} core. It has been demonstrated that the optical interference from dielectric environment significantly modified the Raman scattering of layered MoS2, regardless lattice vibration modes.\cite{Li2012} The author calculated the reflectivity of three different stacking scenarios to estimate the influence of \ce{WO3} and insulating substrate, as shown in. It can be concluded that under 532 nm excitation, the \ce{WO3} core shows little influence on the Raman intensity when \ce{WS2} tube is suspended in air, whereas the \ce{SiO2}/Si substrates will dramatically enhance the Raman scattering of the core-shell NWs. It could be further predicted that current Raman spectra on core-shell NWs can be used to estimate the \ce{WS2} nanotube wall numbers.

@@
